### 2021-09-26 paper/output/document/paper32.tex
added maxim

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
In order to make this true, we'd have to require that everything is either obligatory or
prohibited somewhere. Sadly, that breaks everything and destroys the 
notion of permissibility everywhere \footnote{See Appendix for an examination of a buggy version of DDL that led to this insight.}. 
If something breaks later in this section, it may be because of vacuous permissibility.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ contradictory{\isacharunderscore}obs{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{$\color{blue} $Nitpick found a counterexample for card i = 1:

  Free variables:
    A = ($\lambda x. \_$)($i_1$ := True)
    B = ($\lambda x. \_$)($i_1$ := True) $\color{blue}$%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Contradictory things can't be obligated in Kr, since a contradiction can't be true at any deontic alternative.
This doesn't hold in DDL, and we already saw this cause problems for the naive formalization. We should 
expect those problems to hold in our implementation of Kr, but this difference suggests that they are 
a symptom of DDL, not of any inherent problem with Kroy's formalization.%
\end{isamarkuptext}\isamarkuptrue%
%
\emph{Obligatory statements should be permissible}
%
\begin{isamarkuptext}%
Kr includes the intuitively appealing theorem that if a statement is obligated at a world, then it 
is permissible at that world\footnote{This follows straightforwardly from the Kripke semantics. If proposition $A$ is 
obligated at world $w$, this means that at all of $w$'s neighbors, $O A$ holds. Therefore, 
$\exists w'$ such that $w$ sees $w'$ and $O A$ holds at $w'$ so $A$ is permissible at $w$.}. Let's see 
if that also holds in DDL.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ ob{\isacharunderscore}implies{\isacharunderscore}perm{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ w\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Just as with the naive formalization, Kroy's formalization allows for contradictory obligations. 
        Recall earlier that I showed this is a property of DDL itself. This is a good goal to have in mind when 
        developing my custom formalization.

        Next, I will test the stronger property that if two maxims imply a
        contradiction, they may not be simultaneously willed.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}A\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ B{\isacharparenright}{\isacharparenright}w{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2 and card s = 1:

  Free variables:
    A = ($\lambda x. \_$)($i_1$ := True, $i_2$  := False)
    B = ($\lambda x. \_$)($i_1$  := True, $i_2$  := False)
    w = $i_2$ \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
        DDL itself allows implied contradictions and, as I explored in Section \ref{sec:naive_tests_kroy}, Kroy's 
        formalization doesn't do anything to remedy this. IS THIS ACTUALLY HOW WE REPRESENT A CONTRADICTION

@@

%:%240=131%:%

@@

%:%242=132%:%
%:%243=133%:%
%:%244=134%:%
%:%245=135%:%

@@

%:%248=135%:%
%:%252=135%:%
%:%253=135%:%
%:%255=136%:%
%:%256=137%:%
%:%257=138%:%
%:%258=139%:%
%:%259=140%:%
%:%269=142%:%
%:%270=143%:%
%:%271=144%:%
%:%272=145%:%
%:%275=147%:%

@@

%:%279=150%:%
%:%280=151%:%
%:%281=152%:%
%:%282=153%:%
%:%284=155%:%
%:%285=155%:%
%:%286=156%:%
%:%287=157%:%
%:%288=158%:%
%:%289=158%:%
%:%291=158%:%
%:%295=158%:%
%:%296=158%:%
%:%298=159%:%
%:%299=160%:%
%:%300=161%:%
%:%301=162%:%
%:%311=164%:%
%:%312=165%:%
%:%321=170%:%
%:%333=172%:%
%:%334=173%:%
%:%335=174%:%
%:%336=175%:%
%:%337=176%:%
%:%339=177%:%
%:%340=177%:%
%:%341=178%:%
%:%343=179%:%
%:%344=180%:%
%:%345=181%:%
%:%348=183%:%
%:%350=185%:%

@@

%:%352=186%:%
%:%353=187%:%
%:%354=187%:%
%:%356=187%:%
%:%360=187%:%
%:%361=187%:%
%:%363=188%:%
%:%364=189%:%
%:%365=190%:%
%:%366=191%:%
%:%367=192%:%
%:%368=193%:%
%:%378=195%:%
%:%380=197%:%
%:%381=197%:%
%:%383=199%:%
%:%385=201%:%
%:%386=201%:%
%:%387=201%:%
%:%389=201%:%
%:%393=201%:%
%:%394=201%:%
%:%396=202%:%
%:%397=203%:%
%:%398=204%:%
%:%399=205%:%
%:%409=207%:%
%:%410=208%:%

@@

%:%412=210%:%
%:%421=213%:%
%:%433=215%:%
%:%434=216%:%
%:%435=217%:%
%:%436=218%:%
%:%437=219%:%
%:%438=220%:%
%:%439=221%:%
%:%440=222%:%
%:%441=223%:%
%:%445=225%:%
%:%449=227%:%
%:%450=228%:%
%:%451=229%:%
%:%453=231%:%
%:%454=231%:%

@@

%:%457=232%:%
%:%458=233%:%
%:%459=234%:%
%:%460=234%:%
%:%461=235%:%
%:%464=236%:%
%:%468=236%:%
%:%469=236%:%
%:%471=237%:%
%:%472=238%:%
%:%482=240%:%
%:%483=241%:%
%:%484=242%:%
%:%485=243%:%
%:%486=244%:%
%:%487=245%:%
%:%488=246%:%
%:%489=247%:%
%:%490=248%:%
%:%491=249%:%
%:%492=250%:%
%:%493=251%:%
%:%494=252%:%
%:%495=253%:%
%:%496=254%:%
%:%500=256%:%
%:%501=257%:%
%:%503=259%:%
%:%504=259%:%
%:%506=260%:%
%:%507=260%:%
%:%508=261%:%
%:%509=262%:%
%:%510=262%:%
%:%511=263%:%
%:%514=264%:%
%:%518=264%:%
%:%519=264%:%

@@

%:%521=265%:%
%:%522=266%:%
%:%523=266%:%
%:%524=267%:%
%:%525=267%:%
%:%526=267%:%
%:%527=268%:%
%:%537=270%:%
%:%538=271%:%
%:%539=272%:%
%:%540=273%:%
%:%544=275%:%
%:%548=277%:%
%:%549=278%:%
%:%550=279%:%
%:%554=281%:%
%:%555=282%:%
%:%557=284%:%
%:%558=284%:%
%:%571=305%:%
%:%572=306%:%
%:%573=306%:%
%:%575=307%:%
%:%576=308%:%
%:%577=309%:%
%:%578=310%:%
%:%579=311%:%
%:%580=312%:%
%:%581=312%:%
%:%583=313%:%
%:%584=314%:%
%:%585=314%:%
%:%586=315%:%
%:%587=316%:%
%:%588=316%:%
%:%590=317%:%
%:%591=318%:%

@@

%:%595=321%:%
%:%597=323%:%

@@

%:%601=325%:%
%:%603=325%:%
%:%607=325%:%
%:%608=325%:%
%:%610=326%:%
%:%611=327%:%
%:%612=328%:%
%:%613=329%:%
%:%614=330%:%
%:%615=331%:%
%:%616=332%:%
%:%626=334%:%
%:%627=335%:%
%:%628=336%:%
%:%631=338%:%
%:%632=339%:%
%:%633=340%:%
%:%634=341%:%
%:%635=342%:%
%:%636=343%:%
%:%639=345%:%
%:%641=347%:%
%:%642=347%:%
%:%643=348%:%
%:%646=349%:%
%:%650=349%:%
%:%651=349%:%
%:%653=350%:%
%:%659=350%:%

@@

%:%664=352%:%
%:%665=353%:%
%:%666=354%:%
%:%667=355%:%
%:%668=355%:%
%:%670=355%:%
%:%674=355%:%
%:%675=355%:%
%:%677=356%:%
%:%678=357%:%
%:%679=358%:%
%:%680=359%:%
%:%681=360%:%
%:%691=362%:%
%:%692=363%:%
%:%693=364%:%
%:%694=365%:%
%:%695=366%:%
%:%696=367%:%
%:%697=368%:%
%:%698=369%:%
%:%699=370%:%
%:%703=373%:%
%:%704=374%:%
%:%705=375%:%

@@

%:%710=380%:%
%:%711=381%:%
%:%712=382%:%
%:%713=383%:%
%:%714=384%:%
%:%723=386%:%
%:%735=388%:%
%:%736=389%:%
%:%737=390%:%
%:%739=392%:%
%:%740=392%:%
%:%741=393%:%
%:%742=394%:%
%:%743=395%:%
%:%744=395%:%
%:%746=395%:%
%:%750=395%:%
%:%751=395%:%
%:%753=396%:%
%:%754=397%:%
%:%755=398%:%
%:%756=399%:%
%:%766=401%:%
%:%767=402%:%
%:%768=403%:%
%:%772=405%:%
%:%774=407%:%
%:%775=407%:%
%:%776=408%:%
%:%777=409%:%
%:%778=410%:%
%:%779=410%:%
%:%781=410%:%
%:%785=410%:%
%:%786=410%:%

@@

%:%789=412%:%
%:%790=413%:%
%:%791=414%:%

@@

%:%802=417%:%
%:%804=419%:%
%:%805=419%:%
%:%806=420%:%
%:%807=421%:%
%:%808=422%:%
%:%809=422%:%
%:%811=422%:%
%:%815=422%:%
%:%816=422%:%
%:%818=423%:%
%:%819=424%:%
%:%820=425%:%
%:%821=426%:%
%:%822=427%:%
%:%832=429%:%
%:%833=430%:%
%:%835=432%:%
%:%836=432%:%
%:%837=433%:%
%:%838=434%:%
%:%841=435%:%
%:%845=435%:%
%:%846=435%:%
%:%847=435%:%

@@

%:%857=438%:%
%:%858=439%:%
%:%859=440%:%
%:%861=442%:%
%:%862=442%:%
%:%863=443%:%
%:%864=444%:%
%:%867=445%:%
%:%871=445%:%
%:%872=445%:%
%:%873=445%:%

@@

%:%890=453%:%
%:%892=453%:%
%:%896=453%:%
%:%897=453%:%
%:%899=454%:%

@@

%:%912=459%:%
%:%913=460%:%
%:%914=461%:%

@@

@@

%:%920=466%:%
%:%921=467%:%
%:%922=468%:%

@@

%:%925=470%:%
%:%927=470%:%
%:%931=470%:%
%:%932=470%:%
%:%934=471%:%
%:%935=472%:%
%:%936=473%:%
%:%937=474%:%
%:%938=475%:%
%:%939=476%:%
%:%949=478%:%
%:%950=479%:%
%:%951=480%:%
%:%952=481%:%
%:%953=482%:%
%:%954=483%:%
%:%956=485%:%
%:%957=485%:%
%:%958=486%:%
%:%959=487%:%
%:%962=488%:%
%:%966=488%:%
%:%967=488%:%
%:%969=489%:%
%:%979=491%:%
%:%980=492%:%
%:%981=493%:%
%:%982=494%:%
%:%991=496%:%
%:%1003=498%:%
%:%1004=499%:%
%:%1005=500%:%
%:%1006=501%:%
%:%1010=503%:%
%:%1011=504%:%
%:%1013=506%:%

@@

%:%1017=508%:%
%:%1018=509%:%
%:%1021=510%:%
%:%1025=510%:%
%:%1026=510%:%
%:%1027=510%:%
%:%1029=511%:%
%:%1030=512%:%
%:%1040=514%:%
%:%1041=515%:%
%:%1042=516%:%
%:%1043=517%:%
%:%1044=518%:%
%:%1045=519%:%
%:%1046=520%:%
%:%1047=521%:%
%:%1048=522%:%
%:%1049=523%:%
%:%1050=524%:%

@@

%:%1056=530%:%
%:%1057=530%:%
%:%1058=531%:%
%:%1059=532%:%
%:%1060=533%:%
%:%1061=533%:%
%:%1063=533%:%
%:%1067=533%:%
%:%1068=533%:%
%:%1070=534%:%
%:%1071=535%:%
%:%1072=536%:%
%:%1073=537%:%
%:%1074=538%:%
%:%1075=539%:%
%:%1085=541%:%
%:%1086=542%:%
%:%1087=543%:%
%:%1088=544%:%
%:%1092=546%:%
%:%1093=547%:%
%:%1094=548%:%
%:%1096=550%:%
%:%1097=550%:%
%:%1098=551%:%
%:%1099=551%:%
%:%1101=552%:%
%:%1102=553%:%
%:%1103=553%:%
%:%1104=554%:%
%:%1105=555%:%
%:%1106=555%:%
%:%1107=556%:%
%:%1110=557%:%
%:%1114=557%:%
%:%1115=557%:%
%:%1117=558%:%
%:%1118=559%:%
%:%1119=560%:%
%:%1129=562%:%
%:%1130=563%:%
%:%1131=564%:%
%:%1132=565%:%
%:%1134=567%:%
%:%1135=567%:%
%:%1136=568%:%
%:%1138=568%:%
%:%1142=568%:%
%:%1143=568%:%
%:%1145=569%:%
%:%1153=569%:%
%:%1154=570%:%
%:%1155=571%:%
%:%1156=571%:%
%:%1157=572%:%
%:%1159=572%:%
%:%1163=572%:%
%:%1164=572%:%
%:%1166=573%:%
%:%1176=575%:%
%:%1177=576%:%
%:%1178=577%:%

>>>>

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
In order to make this true, we'd have to require that everything is either obligatory or
prohibited somewhere. Sadly, that breaks everything and destroys the 
notion of permissibility everywhere \footnote{See Appendix for an examination of a buggy version of DDL that led to this insight.}. 
If something breaks later in this section, it may be because of vacuous permissibility.%
\end{isamarkuptext}\isamarkuptrue%
%
\emph{Obligatory statements should be permissible}
%
\begin{isamarkuptext}%
Kr includes the intuitively appealing theorem that if a statement is obligated at a world, then it 
is permissible at that world\footnote{This follows straightforwardly from the Kripke semantics. If proposition $A$ is 
obligated at world $w$, this means that at all of $w$'s neighbors, $O A$ holds. Therefore, 
$\exists w'$ such that $w$ sees $w'$ and $O A$ holds at $w'$ so $A$ is permissible at $w$.}. Let's see 
if that also holds in DDL.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ ob{\isacharunderscore}implies{\isacharunderscore}perm{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ w\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Just as with the naive formalization, Kroy's formalization allows for contradictory obligations. 
        Testing this lemma in DDL without the FUL shows that this is a property of DDL itself. This is a good goal to have in mind when 
        developing my custom formalization.

        Next, I will test the stronger property that if two maxims imply a
        contradiction, they may not be simultaneously willed.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2 and card s = 1:

  Free variables:
    A = ($\lambda x. \_$)($i_1$ := True, $i_2$  := False)
    B = ($\lambda x. \_$)($i_1$  := True, $i_2$  := False)
    w = $i_2$ \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
        DDL itself allows implied contradictions and, as I explored in Section \ref{sec:naive_tests_kroy}, Kroy's 
        formalization doesn't do anything to remedy this.

@@

@@

%:%244=133%:%
%:%245=134%:%

@@

%:%247=136%:%
%:%248=137%:%
%:%250=139%:%
%:%251=139%:%
%:%252=140%:%
%:%253=141%:%
%:%254=142%:%
%:%255=142%:%
%:%257=142%:%
%:%261=142%:%
%:%262=142%:%
%:%264=143%:%
%:%265=144%:%
%:%266=145%:%
%:%267=146%:%
%:%277=148%:%

@@

%:%287=154%:%
%:%299=156%:%
%:%300=157%:%
%:%301=158%:%
%:%302=159%:%
%:%303=160%:%
%:%305=161%:%
%:%306=161%:%
%:%307=162%:%
%:%309=163%:%
%:%310=164%:%
%:%311=165%:%
%:%314=167%:%
%:%316=169%:%
%:%317=169%:%
%:%318=170%:%
%:%319=171%:%
%:%320=171%:%
%:%322=171%:%
%:%326=171%:%
%:%327=171%:%
%:%329=172%:%
%:%330=173%:%
%:%331=174%:%
%:%332=175%:%
%:%333=176%:%
%:%334=177%:%
%:%344=179%:%
%:%346=181%:%
%:%347=181%:%
%:%349=183%:%

@@

%:%352=185%:%
%:%353=185%:%
%:%355=185%:%
%:%359=185%:%
%:%360=185%:%
%:%362=186%:%
%:%363=187%:%
%:%364=188%:%
%:%365=189%:%
%:%375=191%:%
%:%376=192%:%
%:%377=193%:%
%:%378=194%:%
%:%387=197%:%
%:%399=199%:%
%:%400=200%:%
%:%401=201%:%
%:%402=202%:%
%:%403=203%:%
%:%404=204%:%
%:%405=205%:%
%:%406=206%:%
%:%407=207%:%

@@

%:%415=211%:%
%:%416=212%:%
%:%417=213%:%
%:%419=215%:%
%:%420=215%:%
%:%422=216%:%
%:%423=216%:%
%:%424=217%:%
%:%425=218%:%
%:%426=218%:%
%:%427=219%:%
%:%430=220%:%
%:%434=220%:%
%:%435=220%:%
%:%437=221%:%
%:%438=222%:%
%:%448=224%:%
%:%449=225%:%
%:%450=226%:%
%:%451=227%:%
%:%452=228%:%
%:%453=229%:%
%:%454=230%:%
%:%455=231%:%

@@

%:%457=233%:%
%:%458=234%:%
%:%459=235%:%
%:%460=236%:%
%:%461=237%:%
%:%462=238%:%
%:%466=240%:%
%:%467=241%:%
%:%469=243%:%
%:%470=243%:%
%:%472=244%:%
%:%473=244%:%
%:%474=245%:%
%:%475=246%:%
%:%476=246%:%
%:%477=247%:%
%:%480=248%:%
%:%484=248%:%
%:%485=248%:%
%:%486=249%:%
%:%487=249%:%
%:%488=250%:%
%:%489=250%:%
%:%490=251%:%
%:%491=251%:%
%:%492=251%:%
%:%493=252%:%
%:%503=254%:%
%:%504=255%:%
%:%505=256%:%
%:%506=257%:%
%:%510=259%:%
%:%514=261%:%
%:%515=262%:%
%:%516=263%:%

@@

%:%521=266%:%
%:%523=268%:%
%:%524=268%:%
%:%537=289%:%
%:%538=290%:%
%:%539=290%:%
%:%541=291%:%
%:%542=292%:%
%:%543=293%:%
%:%544=294%:%
%:%545=295%:%
%:%546=296%:%
%:%547=296%:%
%:%549=297%:%
%:%550=298%:%
%:%551=298%:%
%:%552=299%:%
%:%553=300%:%
%:%554=300%:%
%:%556=301%:%
%:%557=302%:%
%:%560=304%:%
%:%561=305%:%
%:%563=307%:%
%:%564=307%:%
%:%565=308%:%
%:%566=309%:%
%:%567=309%:%
%:%569=309%:%
%:%573=309%:%
%:%574=309%:%
%:%576=310%:%
%:%577=311%:%
%:%578=312%:%
%:%579=313%:%
%:%580=314%:%
%:%581=315%:%
%:%582=316%:%
%:%592=318%:%
%:%593=319%:%

@@

%:%597=322%:%

@@

%:%601=326%:%
%:%602=327%:%
%:%605=329%:%
%:%607=331%:%
%:%608=331%:%
%:%609=332%:%
%:%612=333%:%
%:%616=333%:%
%:%617=333%:%
%:%619=334%:%
%:%625=334%:%
%:%628=335%:%
%:%629=336%:%
%:%630=336%:%
%:%631=337%:%
%:%632=338%:%
%:%633=339%:%
%:%634=339%:%
%:%636=339%:%
%:%640=339%:%
%:%641=339%:%
%:%643=340%:%
%:%644=341%:%
%:%645=342%:%
%:%646=343%:%
%:%647=344%:%
%:%657=346%:%
%:%658=347%:%
%:%659=348%:%
%:%660=349%:%
%:%661=350%:%

@@

%:%664=353%:%
%:%665=354%:%
%:%669=357%:%
%:%670=358%:%
%:%671=359%:%
%:%672=360%:%
%:%673=361%:%
%:%674=362%:%
%:%675=363%:%
%:%676=364%:%
%:%677=365%:%
%:%678=366%:%
%:%679=367%:%
%:%680=368%:%
%:%689=370%:%
%:%701=372%:%
%:%702=373%:%
%:%703=374%:%
%:%705=376%:%

@@

%:%710=379%:%
%:%712=379%:%
%:%716=379%:%
%:%717=379%:%
%:%719=380%:%
%:%720=381%:%
%:%721=382%:%
%:%722=383%:%
%:%732=385%:%
%:%733=386%:%
%:%734=387%:%
%:%738=389%:%
%:%740=391%:%
%:%741=391%:%
%:%742=392%:%
%:%743=393%:%
%:%744=394%:%
%:%745=394%:%
%:%747=394%:%
%:%751=394%:%
%:%752=394%:%
%:%754=395%:%
%:%755=396%:%
%:%756=397%:%
%:%757=398%:%
%:%767=400%:%
%:%768=401%:%
%:%770=403%:%
%:%771=403%:%
%:%772=404%:%
%:%773=405%:%
%:%774=406%:%
%:%775=406%:%
%:%777=406%:%
%:%781=406%:%
%:%782=406%:%
%:%784=407%:%
%:%785=408%:%
%:%786=409%:%
%:%787=410%:%

@@

%:%798=413%:%
%:%799=414%:%

@@

%:%802=416%:%
%:%803=417%:%
%:%804=418%:%
%:%807=419%:%
%:%811=419%:%
%:%812=419%:%
%:%813=419%:%
%:%822=421%:%
%:%823=422%:%
%:%824=423%:%
%:%825=424%:%
%:%827=426%:%
%:%828=426%:%
%:%829=427%:%
%:%830=428%:%
%:%833=429%:%
%:%837=429%:%
%:%838=429%:%
%:%839=429%:%
%:%848=431%:%
%:%849=432%:%
%:%851=434%:%
%:%852=434%:%
%:%853=435%:%
%:%854=436%:%
%:%855=437%:%

@@

%:%858=437%:%
%:%862=437%:%
%:%863=437%:%
%:%865=438%:%
%:%866=439%:%
%:%867=440%:%
%:%868=441%:%
%:%878=443%:%
%:%879=444%:%
%:%880=445%:%
%:%881=446%:%

@@

%:%890=454%:%
%:%891=454%:%
%:%893=454%:%
%:%897=454%:%
%:%898=454%:%

@@

%:%903=458%:%
%:%904=459%:%
%:%905=460%:%

@@

%:%918=465%:%

@@

%:%920=467%:%
%:%922=469%:%

@@

%:%925=471%:%
%:%928=472%:%
%:%932=472%:%
%:%933=472%:%
%:%935=473%:%
%:%945=475%:%
%:%946=476%:%
%:%947=477%:%
%:%948=478%:%
%:%957=480%:%
%:%969=482%:%
%:%970=483%:%
%:%971=484%:%
%:%972=485%:%
%:%976=487%:%
%:%977=488%:%
%:%979=490%:%
%:%980=490%:%
%:%981=491%:%
%:%982=492%:%
%:%983=492%:%
%:%984=493%:%
%:%987=494%:%
%:%991=494%:%
%:%992=494%:%
%:%993=494%:%
%:%995=495%:%
%:%996=496%:%
%:%1006=498%:%
%:%1007=499%:%
%:%1008=500%:%
%:%1009=501%:%
%:%1010=502%:%
%:%1011=503%:%
%:%1012=504%:%
%:%1013=505%:%

@@

%:%1017=509%:%
%:%1018=510%:%
%:%1019=511%:%
%:%1020=512%:%
%:%1022=514%:%
%:%1023=514%:%
%:%1024=515%:%
%:%1025=516%:%
%:%1026=517%:%
%:%1027=517%:%
%:%1029=517%:%
%:%1033=517%:%
%:%1034=517%:%
%:%1036=518%:%
%:%1037=519%:%
%:%1038=520%:%
%:%1039=521%:%
%:%1040=522%:%
%:%1041=523%:%

@@

%:%1058=530%:%
%:%1059=531%:%
%:%1060=532%:%
%:%1062=534%:%
%:%1063=534%:%
%:%1064=535%:%
%:%1065=535%:%
%:%1067=536%:%
%:%1068=537%:%
%:%1069=537%:%
%:%1070=538%:%
%:%1071=539%:%
%:%1072=539%:%
%:%1073=540%:%
%:%1076=541%:%
%:%1080=541%:%
%:%1081=541%:%
%:%1083=542%:%
%:%1084=543%:%
%:%1085=544%:%
%:%1095=546%:%
%:%1096=547%:%
%:%1097=548%:%
%:%1098=549%:%
%:%1100=551%:%
%:%1101=551%:%
%:%1102=552%:%
%:%1104=552%:%
%:%1108=552%:%
%:%1109=552%:%
%:%1111=553%:%
%:%1119=553%:%
%:%1120=554%:%
%:%1121=555%:%
%:%1122=555%:%
%:%1123=556%:%
%:%1125=556%:%
%:%1129=556%:%
%:%1130=556%:%
%:%1132=557%:%
%:%1142=559%:%
%:%1143=560%:%
%:%1144=561%:%
